---
title: "Alcohol vs Seat choice"
author: "Jamie Santiago"
date: "Summer 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

Based on the boxplot, the median of people who sit in the back as I see it is higher than both the third quantile of people who sit in the front and the third quantile who sit in the middle.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The third quantile of the front is 2 and the third quantile of the middle is 3. The median of the back is 4 so in this case the median is higher than the third quantile of both the front and middle. 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)

After running the inferential test we find that the probability of the people in front and middle consuming the same amount of alcohol that people in the back being 0.000116. Therefore there is a significant difference of 3.


```{r}
plot(TukeyHSD(model1))
```

## Conclusions


