---
title: "Alcohol vs Seat choice"
author: "Jamie Santiago"
date: "Summer 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

Based on the boxplot, the median of people who sit in the back as I see it is higher than both the third quantile of people who sit in the front and the third quantile who sit in the middle.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The third quantile of the front is 2 and the third quantile of the middle is 3. The median of the back is 4 so in this case the median is higher than the third quantile of both the front and middle. 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

After running the inferential test we find that the probability of the people in front and middle consuming the same amount of alcohol that people in the back being 0.000116. Therefore there is a significant difference of 3.

## When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
```

When looking at the model we see that the middle compared to the back dooes not have 0 in their confidence interval. The same is true when you compare the front and the back. This is also indicative that their is no statistical difference between the front and the middle. The back is different from everyone else.

## Conclusions

When going through the process that's two variables there are more steps that we had to go through which can complicate the process in this assignment. We used ggplot to create the boxplot which showed us the median of how many drinks were consumed per section. Then we ran a numerical summary of the information so we could get exact numbers and see how big the difference actually was. After we ran the interval test to get the probability of these three sections consuming the same amount of alcohol which was 0.000116. We used that comparison model that showed us how significant the difference between each section was. I came to the conclusion that there is in fact a significant difference between how much alcohol the three sections consumed. 
